Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-24 manuscript.tex
some internal review comments

\corr{christoph.wehmeyer@fu-berlin.de}{CW}
%\corr{m.scherer@fu-berlin.de}{MKS}
%\corr{tim.hempel@fu-berlin.de}{TH}
%\corr{simon.olsson@fu-berlin.de}{SO}
%\corr{brookehusic@gmail.com}{BEH}
\corr{frank.noe@fu-berlin.de}{FN}

@@

The underlying software stack for running the tutorial importantly consists of:
\begin{itemize}
\item NumPy -- vectorized operations on multi-dimensional arrays~\cite{numpy}
\item SciPy -- linear algebra, sparse computations~\cite{scipy}
\item Matplotlib -- Visualization~\cite{matplotlib}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization~\cite{pyemma}
\item mdtraj -- reading MD simulation data, calculate observables from MD~\cite{mdtraj}
\end{itemize}

@@

This tutorial consists of nine Jupyter notebooks which introduce the basic features of PyEMMA.
The first notebook (00), which we will summarize in the following, showcases the entire estimation, validation, and analysis workflow.
The goal of this introductory notebook (00) is to provide the user with the typical steps required to obtain a validated MSM analysis of protein or peptide simulation data.
The eight subsequent notebooks (01--08) provide in-depth lessons on specific topics, an introduction to HMMs, and guidelines how to deal with common problems during an MSM estimation.

@@

In short, the workflow consists of extracting molecular features from the raw data (01) which we transform into a suitable, low-dimensional subspace and discretize (02).
Then, we estimate a maximum likelihood or Bayesian MSM from the discrete trajectories and perform validation tests (03).
We can then analize the stationary and kinetic properties of the MSM (04),
find metastable macrostates and apply transition path theory (TPT) to identify the pathways of conformation change (05),
and compute expectation values for experimental observables (06).

@@

\subsection{Estimation and validation}

@@

@@

@@

@@

>>>>

\corr{christoph.wehmeyer@fu-berlin.de}{CW}
%\corr{m.scherer@fu-berlin.de}{MKS}
%\corr{tim.hempel@fu-berlin.de}{TH}
%\corr{simon.olsson@fu-berlin.de}{SO}
%\corr{bhusic@stanford.edu}{BEH}
\corr{frank.noe@fu-berlin.de}{FN}

@@

The underlying software stack for running the tutorial importantly consists of:
\begin{itemize}
% \item NumPy -- vectorized operations on multi-dimensional arrays~\cite{numpy}
% \item SciPy -- linear algebra, sparse computations~\cite{scipy}
% \item Matplotlib -- Visualization~\cite{matplotlib}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter notebook tool used for running the tutorials~\cite{jupyter}, along with extension packages jupyter_contrib_nbextensions and nbexamples
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nguyen2017nglview}
% \item mdtraj -- reading MD simulation data, calculate observables from MD~\cite{mdtraj}
\end{itemize}

@@

This tutorial consists of nine Jupyter notebooks which introduce the basic features of PyEMMA.
The first notebook (00), which we will summarize in the following, showcases the entire estimation, validation, and analysis workflow.
The goal of this introductory notebook (00) is to provide the user with the typical steps required to obtain a validated MSM analysis of protein or peptide simulation data.
The seven subsequent notebooks (01--07) provide in-depth lessons on specific topics, and the last notebook (08) contains guidelines on how to deal with common problems during an MSM estimation.

@@

In short, the workflow consists of:
\begin{itemize}
	\item extracting molecular features from the raw data (01),
	\item transforming those features into a suitable, low-dimensional subspace (02),
	\item discretizing the low-dimensional subsets into a state decomposition (02),
	\item estimating a maximum likelihood or Bayesian MSM from the discrete trajectories and performing validation tests (03),
	\item analyzing the stationary and kinetic properties of the MSM (04),
	\item finding metastable macrostates and applying transition path theory (TPT) to identify the pathways of conformation change (05),
	\item computing expectation values for experimental observables (06), and
	\item coarse-graining the model using a hidden Markov model approach (07).
\end{itemize}

@@

\subsection{Feature selection}

@@

\subsection{Dimensionality reduction}

@@

\subsection{Discretization}

@@

\subsection{MSM estimation and validation}

@@

\subsection{Connecting the MSM with experimental data}
